%!TEX root = ../main.tex
\section{Joint Board Verification Procedure} % (fold)
\label{sec:joint_board_verification_procedure}
This document holds the verification procedure which, when applied succesfully, ensures the correct functionality of the joint board.
Each step is to be followed in the order they are shown to avoid previous faults to propegate throughout the process.
A step consists of an action and the expected outcome of that action.
Any text written with the \texttt{teletype font} refers to signals and pins on the PCB and can be seen on the schematic.
The most recent schematic can be seen appendix \ref{app:joint_board_schem}.

\paragraph{Verify Voltage Rails} % (fold)
 \label{par:verify_voltage_rails}
 \begin{itemize}
 	\item Apply 3.7V to \texttt{VBATT}.
 	\begin{itemize}
 		\item Verify that current draw is within reasonable limits ($<$75 mA). Note that the PCB requires a short pulse of approximately 0.89A while booting.
 		\item Verify 5V and 3.3V voltage rails.
 	\end{itemize}
 \end{itemize}
% paragraph verify_voltage_rails_ (end) 

\paragraph{Verify Voltage Level Shifter Functionality} % (fold)
\label{par:verify_voltage_level_shifter_functionality}
\begin{itemize}
	\item Apply 5V to \texttt{SCLK\_H}.
	\begin{itemize}
		\item  Verify that 3.3V is present on \texttt{SCLK}.
	\end{itemize}
	\item Repeat for signals \texttt{MOSI\_H} and \texttt{RESET\_H}.
	\item Apply 3.3V to \texttt{MISO}.
	\begin{itemize}
		\item  Verify that 5V is present on \texttt{MISO\_H}.
	\end{itemize}
\end{itemize}
% paragraph verify_voltage_level_shifter_functionality (end)

\paragraph{Verify RS-422 Circuitry Functionality} % (fold)
\label{par:verify_rs_422_circuitry_functionality}
\begin{itemize}
	\item Apply 5V to \texttt{A\_N}, 0V to \texttt{A\_P}.
	\begin{itemize}
		\item  Verify that 0V is present on \texttt{A\_H}.
		\item  Verify that 0V is present on \texttt{A}.
	\end{itemize}
	\item Repeat for signal pairs \texttt{B\_N}, \texttt{B\_P} and \texttt{Z\_N}, \texttt{Z\_P}.
	\item Apply 0V to \texttt{A\_N}, 5V to \texttt{A\_P}.
	\begin{itemize}
		\item  Verify that 5V is present on \texttt{A\_H}.
		\item  Verify that 3.3V is present on \texttt{A}.
	\end{itemize}
	\item Repeat for signal pairs \texttt{B\_N}, \texttt{B\_P} and \texttt{Z\_N}, \texttt{Z\_P}.
\end{itemize}
% paragraph verify_rs_422_circuitry_functionality (end)
\paragraph{Verify ATTiny84 Functionality} % (fold)
\label{par:verify_attiny84_functionality}
\begin{itemize}
	\item Load the ATTiny84 with the blink software.
	\begin{itemize}
		\item  Verify that the on-board LED is blinking
	\end{itemize}
\end{itemize}
% paragraph verify_attiny84_functionality (end)
% section joint_board_verification_procedure (end)